A free/open-source Kazakh-Tatar machine translation system

### 2013-04-06 paper/paper.tex
less ERROR

\name{Jonathan North Washington, Francis M. Tyers and Ilnar Salimzyanov}

\address{ Indiana University, Universitat d'Alacant, Kazan Federal University \\
          Bloomington, Alacant, Kazan\\
          IN 47405 (USA), E-03071 Spain, Russia\\
          \email{jonwashi@indiana.edu}, \email{ftyers@dlsi.ua.es},  \email{ilnar.salimzyan@gmail.com} \\
}

@@

\abstract{
This paper presents a bidirectional machine translation system between
Kazakh and Tatar.
 \\
\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
}

\begin{document}
\spacing{1}
\maketitleabstract

>>>>

%FIXME
%\name{Jonathan North Washington, Francis M. Tyers and Ilnar Salimzyanov}

%\address{ Indiana University, Universitat d'Alacant, Kazan Federal University \\
%          Bloomington, Alacant, Kazan\\
%          IN 47405 (USA), E-03071 Spain, Russia\\
%          \email{jonwashi@indiana.edu}, \email{ftyers@dlsi.ua.es},  \email{ilnar.salimzyan@gmail.com} \\
%}

@@

\abstract{
This paper presents a bidirectional machine translation system between
Kazakh and Tatar.
 \\
%FIXME
%\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
}

\begin{document}
\spacing{1}
%FIXME
%\maketitleabstract
